Cancer Applications of Choropleth maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-16 review_article.Rmd
Figures for AUS and editing

# Introduction
<!-- 436 words -->
<!-- What data are we working with, why, what are the purposes -->
Researchers, health authorities, governments and not-for-profits are common communicators of cancer statistics. They often present statistics to the public as aggregated values for geopolitical areas. Presenting these statistics requires aggregating individual observations into the statistics for the geographical units, especially for privacy protection, but also for political and policy purposes.
Data collection or aggregation regions for the amount of cancer diagnoses or excess deaths per area include states, provinces, local government areas, and post/zip codes. To provide the amount, or count, of the diagnoses or excess deaths with these areas, it needs minimal transformation. However, the amount of people living in each of the areas in a set will be different. Those who wish to calculate rates can use the amount of people living in an area as a denominator and the diagnoses can become a numerator to create rates per amount of people. Health registries routinely collect data for public health reasons and may make this available to the public as a service to the community.

<!-- Ways to visualize, whats our hypothesis -->
Choropleth map displays are commonly used for the communication of cancer statistics over geographic domains. In this display, map creators map a statistic to color and apply the colour to the polygons representing geographic regions. Map users may overlook geographic patterns of disease when obscured in a table [@SAMGIS]. Visualizing diseases on maps is often the first step in exploratory spatial data analysis and helps in the formulation of hypotheses. Providing a visual representation of cancer outcomes allows identification, and public health policy and actions can address these patterns. choropleth maps allow the examination of the spatial distribution of the disease incidence, this may reveal a trend in longitude or latitude, differences between rural areas and urban, or coastal and inland areas, or even specific hot spots of the disease. Daniel Exeter [@SE] recognizes that one of the key challenges with mapping spatial patterns of disease is the design of visualizations. This paper considers the current visualization techniques to communicate statistics to members of the public and their applications to cancer statistics. It also considers alternative approaches and compares the visualization methods, highlighting the differences and historic use of these displays.

@@

# Traditional approaches for cancer map displays {#ch:choropleth maps}
<!-- 381 words -->
<!-- what is a choropleth map -->
A choropleth is traditionally used to make a cancer map. It is used to show the geographical distribution of data values by shading areas of a map [@EI]. A choropleth map involves faithfully rendering the geography, and the design of the color scheme and rendering reveal spatial patterns among data values. Identifying and explaining spatial structures, patterns, and processes involve considering the individuals and organizing them into representable units of communities [@SAMGIS]. Early versions of choropleth maps used symbols or patterns instead of color. choropleth maps can be used for displaying disease data [@DMAHP], including cancer data [@CPISACA]. In epidemiology, choropleth maps are often used as a tool to study the spatial distribution of cancer incidence and mortality.

Figure 2<!--\ref{fig:choroCRS}--> shows various geographic projections of choropleth maps of age-adjusted rate (per 100,000 people) of new cases of lung and bronchus in the USA, averaged from 2012 to 2016. The official federal statistics provide cancer incidence and deaths [5], produced by the Centers for Disease Control and Prevention (CDC) and the National Cancer Institute (NCI). The rates exhibit a spatial trend, increasing from west to east. Utah is a spatial outlier, it has a noticeably lower rate than its neighbors. Also, Kentucky and Maine have higher rates than their neighbors. There is possibly a cluster of higher rates around the tobacco states.

<!-- psychology -->
Displaying familiar state boundaries can make a map easier to read [@CIBMUK] and allow viewers to infer the spatial relationships visually in the data using their mental model of the geography.
Consumers of disease displays may include researchers, members of the public, policymakers, and the media  [@CPISACA]. For these consumers, the familiarity of the geography is a worthy consideration when presenting results of spatial analysis.

<!-- potential problems -->
Politically driven boundaries produced the now familiar shapes or regions, this has created individual areas of non-uniform size. These areas have different population densities and are subject to change. 
The different population and geographical sizes of administrative areas can attract attention to the shades of the underpopulated but large areas [@EI], Skowronnek [@BCM] calls this an area-size bias. 
choropleth maps can inhibit visual inference when presenting human-related statistics as the display may draw attention away from the 'potentially more important results in the more populous communities' that are geographically smaller [@SE].

@@

## Cancer atlases {#ch:public}
<!-- 360 words -->
<!-- Displaying of cancer data on choropleth maps -->
A cancer atlas is a map, or collection of maps, representing cancer incidence and mortality for a country or group of countries. Atlases are key to developing hypotheses regarding areas with unusually high rates, geographic correlations, work-related exposures, and high-risk diets [@MACM]. The data collection methods across regions and the administrative control within regions lends itself to choropleth visualization. 
Cancer maps and atlases dating back to Haviland's maps in 1875, and early work in US cancer atlases appearing in 1971 [@burbank]. The presentation of cancer statistics has increased with greater access to computational power and the availability of geographic information systems software [@SE].

<!-- Measures reported in cancer atlases -->
Cancer maps are effective tools for communicating incidence, survival, and mortality to a wide range of audiences, including the general public and others not trained in statistical analysis.
These visualizations enable non-expert audiences to interpret the outputs of sophisticated statistical analysis. Cruickshank (1947) as cited by S. D. Walter [@DMAHP], discusses using visuals as a 'formal statistical assessment of the spatial pattern'. Overwhelmingly, the cancer maps used to communicate to members of the public and other non-expert audiences are choropleth maps.

Epidemiologists and statisticians have developed these statistics over several decades. Mortality rates commonly presented as relative rates of risk across the population and age-adjusted to correct for the higher prevalence of cancers in older populations.
Howe [@HEDP] describes Stock's development of the standardized mortality ratios through the 1930s. Table 1<!--\ref{tab:measures}--> summarizes the measures commonly presented in published cancer atlases.

@@

|Measure |Details| 
|:--------------------|:------------------------------------------------|  
|1. Count| Crude cancer counts|
|2. Rate per 100,000| Cancer incidence per 100,000 population|  
|3. IR (Incidence Ratio)| $(IR)_i=\frac{(Incidence\ Rate)_i}{Average\ Incidence\ Rate}$, |
|| The cancer incidence rate in region $i$ over the average cancer incidence rate for all of the regions|
|4. Age-Adjusted Rate per 100,000| Standardized by age structure or region|   
|5. Age-Adjusted Relative Risk| Standardized by age structure in each region $i$|  
|6. SIR (Standardized Incidence Ratio)| Standardized by incidence in each region $i$|
|7. Below or above Expected| An alternative expression of the SIR|
|8. RER | $RER = \frac{(Cancer\ related\ mortality)_i}{Average\ cancer\ related\ mortality}$|
|(Relative Excess Risk)| Represents the estimate of cancer-related mortality within five years of diagnosis. Also referred to as 'excess hazard ratio'|

<!-- 416 words -->
Roberts [@roberts2019communication] identified 33 publicly available cancer atlases, published between 2010 and 2018, from different countries around the globe. These online atlases used choropleth maps. Non-commercial organizations, including not-for-profits, government, research organizations, advocacy groups or government-funded partnerships published all but one of these. Figure 1<!--\ref{fig:choropleth-grid-create}--> displays a subset of maps from these atlases.

The selection varies in the geographies explored, Figure 1<!--\ref{fig:choropleth-grid-create}-->b, Globocan 2012 [@Globocan] explores Estimated Cancer Incidence, Mortality and Prevalence Worldwide utilizing data sourced from cancer registries of each country. 
The Bowel Cancer Australia Atlas presents an example of a cancer specific atlas, Figure 1<!--\ref{fig:choropleth-grid-create}-->d shows the average Standardized Incidence Ratio of colorectal cancer for Australian males from 2006 to 2010 in Australia [@Bowel]. Like many of the atlases examined, there is a choice of gender displayed in the Bowel Cancer Atlas. An alternative approach used in the Map of Cancer Mortality Rates in Spain, Figure 1<!--\ref{fig:choropleth-grid-create}-->f shows side-by-side maps of the relative risk of lung cancer separately for men and women [@cancerSpain].

There are vast differences in the geographies considered by online atlases. 
Figure 1<!--\ref{fig:choropleth-grid-create}-->b shows global age-standardized incidence rates (per 100,000) for all invasive cancers for both men and women, aggregated at a national level for 2018.
The United States Cancer Statistics [@USInteractive] presented in Figure 1<!--\ref{fig:choropleth-grid-create}-->e contains the incidence rate per 100,000, of all cancer types for men and women in the United States in 2016, aggregated at the state level.
The Environment and Health Atlas of England and Wales, Figure 1<!--\ref{fig:choropleth-grid-create}-->a shows the relative risk for women developing lung cancer in England and Wales in 2010 [@EnvEnglandWales2] at a neighborhood (small-area) scale.
The Atlas of Cancer in Queensland, Figure 1<!--\ref{fig:choropleth-grid-create}-->c shows the relative incidence ratio of lung cancer in males for each Statistical Area at Level 2 in the state of Queensland within Australia [@QLDcancerAtlas].

Age-specific atlases are less common, Figure 1<!--\ref{fig:choropleth-grid-create}-->g displays Atlas of Childhood Cancer in Ontario, this communicates the incidence rate of childhood cancers per 100,000 (by census division) for children aged 0-14, in Ontario from 1995 to 2004 [@OntarioPediatric]. This atlas communicates information regarding a tiny geographic region.

## Additional materials
<!-- 479 words -->
Including supplementary graphs and plots add more depth and information. Additional materials such as tables, graphs, and text explanations, support the understanding and inference derived from maps, ensuring the message communicated will be consistent across a range of viewers [@CPISACA]. The many displays of statistical summaries, including dot plots, bar plots, box plots, cumulative distribution plots, scatter plots, normal probability plots, can provide alternative views of the cancer statistics. These can also display supporting statistics such as error, confidence intervals, distributions, sample or population sizes, standard deviation. When presenting cancer maps the display of the supplementary statistics helps. The intuition derived from maps must be ‘validated by rigorous statistical analyses’ [@MACM].

@@

Map users can define the population further using the demographics of the individuals within each area.  Demographics that can influence cancer rates include information regarding the age and sex distribution of the areas presented. Some digital atlases surveyed allow users to control the display to select subsets such as males, females or those aged over 65. 
Similarly, socioeconomic indicators, such as unemployment rates, poverty rates, remoteness, and education levels,  can explain how the experience of cancer prevalence varies for various members of society. Few atlases provide this level of detail.
Introducing population and demographic information helps to interpret the rates in areas effectively, but there will still be uncertainty around the rates.
To address this, cancer atlases often communicate uncertainty about the value of a statistic. Cancer atlas creators may introduce uncertainty when using samples, or there are errors occurring in the disease reporting, or models are used to simulate values to maintain privacy. The statistics that report on uncertainty include sample or population size, standard deviation, confidence intervals, statistical significance, quantiles, and  credible intervals. The most common measures used to represent uncertainty were credible or confidence intervals (CIs). Displaying the uncertainty associated with reported statistics is a vital feature of a cancer map, but it is difficult to display effectively. The map focuses on displaying the statistic and lacks additional space to represent the uncertainty. Providing an adjacent map or overlaying maps with symbols [@VSSDCUC] are two approaches.

@@

The administrative boundaries used to define regions may limit a choropleth display.
Those who critique choropleth maps often dicuss election mapping, where each electorate decides the outcome of one parliamentary seat in the house of representatives.
While all states are visible in a map display of Australia, smaller regions such as electorates present an urban-rural divide, where rural regions are much larger than metropolitan areas of similar or greater populations. 
The landmass occupied by urban electoral districts is only 10% of Australia, yet 90% of the population live in these urban areas. To present election results on a choropleth map should be 'unthinkable',XXX as it means diminishing the visual impact of most of the electorates.
Using a map of Australia as a visual statistic would communicate an incorrect distribution of votes across the country.

Spatially heterogeneous population distribution across a country's landmass is an issue common to many countries, especially British colonies [@ACTUC]. However, the boundaries shown in choropleth maps provide a familiar display. This may be less threatening to an audience that could be unfamiliar was interpreting spatial statistics, even though they suffer primarily from unfaithfully representing the disease information by hiding small geographic areas. Inset maps like in Brisbane city in Figure 1<!--\ref{fig:choropleth-grid-create}-->c of the state of Queensland are commonly used to reduce distorted interpretations, but it is a band aid remedy. 
As this feature of population distributions continues to intensify, the need for cartograms as an alternative to a choropleth map should only increase.

@@

<!-- What is a cartogram? -->
choropleth maps imply uniformity of data across the geographic space but population densities are unlikely to be uniform [@BCM]. Cartographers developed the cartogram to draw the attention to the population by transforming the map [@ACCAC]. The resulting display can communicate the impact of the disease more accurately across the population, as recorded by the statistic, at the sacrifice of geographic accuracy.

<!-- There are many alternative views of the world-->
<!-- Tobler map projections - I think this is not relevant here
choropleth maps may be considered true topological maps however,, if the landmass displayed covers enough of the globe, there must be a transformation or distortion to display the land in 2D [@HTLWM]. The amount of distortion is related to the distance covered by the landmass displayed @GAMP.
World map projections reflect the frequent perspectives used to view the earth. Choropleth maps will always be distorted if they cover enough of the globe, just like photographs of the globe from space. Choropleth creation requires choosing a map projection that shows a favorable distortion of the geography for presenting the set of spatial information. Selecting a display can prevent misinterpretation of global statistics, as global maps face the challenge of equitable displays of landmass on maps [@RSCW].
If the statistic presented on the map base relies on physical distance and is influenced by the topology there is no transformation needed, beyond choosing a reasonable projection. 
-->

>>>>

# Introduction
<!-- 436 words -->
<!-- What data are we working with, why, what are the purposes -->
Researchers, health authorities, governments, not-for-profits and the media are common communicators of cancer statistics. They often present statistics to the public as aggregated values for geopolitical areas. Presenting these statistics requires aggregating individual observations for the geographical units, especially for privacy protection, but also for political and policy purposes. Examples of typical geographical units include states, provinces, local government areas, and post/zip codes. It is easy to provide counts of the diagnoses or excess deaths within these areas. However, the amount of people living in each of the areas in a set of areas will be different. Calculating incidence rates involves dividing the count by the population for each area, for example, the rate per 100000 people. Counts and population datasets are collected routinely for public health reasons and may be made available to the general public as a service to the community.

<!-- Ways to visualize, whats our hypothesis -->
To visualize and communicate geospatial cancer statistics over geographic domain, a choropleth map is the common display. Choropleth maps show polygons representing the geographic units, where each polygon is shaded with a color according to the area-specific values of the statistic being conveyed. Visualizing this data is helpful as geographic patterns of disease may be obscured when reported in a table [@SAMGIS]. Providing a visual representation of cancer outcomes allows identification of geographic patterns of the disease that can then be addressed with public health policy and actions. The spatial distribution of the disease incidence can be examined using a choropleth and may reveal a trend in longitude or latitude, or rural vs urban, or coastal vs inland, or even specific hot spots of the disease. One of the key challenges with mapping spatial patterns of disease is the design of visualizations [@SE]. It is important to consider the strengths and weaknesses of designs, as visualizing diseases on maps is often the first step in exploratory spatial data analysis and helps in the formulation of hypotheses. This paper considers the current visualization techniques to communicate statistics to the public and their applications to cancer statistics. Alternative approaches are also considered, and the limitations of the visualization methods, highlighting the differences and historic use of these displays.

@@

# Traditional approaches for cancer map displays {#ch:choropleth maps}
<!-- 381 words -->
<!-- what is a choropleth map -->
A choropleth map displays the geographical distribution of data over a set of spatial units by shading areas of a map [@EI, @BCM]. Faithful rendering of the geography, when combined with an appropriate color scheme, can reveal spatial patterns among data values. Identifying and explaining spatial structures, patterns, and processes involve considering the individuals and organizing them into representable units of communities [@SAMGIS]. Early versions of choropleth maps used symbols or patterns instead of color. Choropleth maps can be used for displaying disease data [@DMAHP], including cancer data [@CPISACA]. In epidemiology, choropleth maps are often used as a tool to study the spatial distribution of cancer incidence and mortality.

<!-- psychology -->
Displaying familiar state boundaries can make a map easier to read [@CIBMUK] and allow viewers to infer the spatial relationships visually in the data using their mental model of the geography. The map users of disease displays may include researchers, the public, policymakers, and the media [@CPISACA]. For these users, the familiarity of the geography is a worthy consideration when presenting results of spatial analysis.

@@

## Cancer atlases {#ch:public}
<!-- 360 words -->
<!-- Displaying of cancer data on choropleth maps -->
A cancer atlas is a map, or collection of maps, representing cancer incidence and mortality for a country, or group of countries. Atlases are key to developing hypotheses regarding areas with unusually high rates, geographic correlations, work-related exposures, and high-risk diets [@MACM]. The data collection methods across regions and the administrative control within regions lends itself to choropleth visualization. 
Cancer maps and atlases dating back to Haviland's maps in 1875, and early work in US cancer atlases appearing in 1971 [@burbank]. The presentation of cancer statistics has increased with greater access to computational power and the availability of geographic information systems software [@SE].

<!-- Measures reported in cancer atlases -->
Cancer maps are effective tools for communicating incidence, survival, and mortality to a wide range of audiences, including the public and others not trained in statistical analysis.
These visualizations enable non-expert audiences to interpret the outputs of sophisticated statistical analysis. Cruickshank (1947) as cited by S. D. Walter [@DMAHP], discusses using visuals as a 'formal statistical assessment of the spatial pattern'. Overwhelmingly, the cancer maps used to communicate to members of the public and other non-expert audiences are choropleth maps.

Epidemiologists and statisticians have developed the statistics used to communicate the burden of cancer over several decades. Table 1<!--\ref{tab:measures}--> summarizes the measures commonly presented in published cancer atlases. Mortality rates are commonly presented as relative rates of risk across the population and age-adjusted to correct for the higher prevalence of cancers in older populations.
Howe [@HEDP] describes Stock's development of the standardized mortality ratios through the 1930s.

@@

|Measure |Details| 
|:--------------------|:------------------------------------------------|  
|1. Count| Crude cancer counts|
|2. Rate per 100,000| Cancer incidence per 100,000 population|  
|3. IR (Incidence Ratio)| $(IR)_i=\frac{(Incidence\ Rate)_i}{Average\ Incidence\ Rate}$, |
|| The cancer incidence rate in region $i$ over the average cancer incidence rate for all of the regions|
|4. Age-Adjusted Rate per 100,000| Standardized by age structure or region|   
|5. Age-Adjusted Relative Risk| Standardized by age structure in each region $i$|  
|6. SIR (Standardized Incidence Ratio)| Incidence standardized by population at risk in each region $i$|
|7. Below or above Expected| An alternative expression of the SIR|
|8. RER | $RER = \frac{(Cancer\ related\ mortality)_i}{Average\ cancer\ related\ mortality}$|
|(Relative Excess Risk)| Represents the estimate of cancer-related mortality within five years of diagnosis. Also referred to as 'excess hazard ratio'|

<!-- 416 words -->
Roberts [@roberts2019communication] identified 33 cancer atlases published between 2010 and 2018. Each of these online atlases uses choropleth maps. All except one of these were published by non-commercial organizations, including not-for-profits, government, research organizations, advocacy groups or government-funded partnerships. Figure 1<!--\ref{fig:choropleth-grid-create}--> displays a subset of maps from these atlases, the selection varies in the geographies explored. Figure 1<!--\ref{fig:choropleth-grid-create}-->b shows Globocan 2012 [@Globocan] which explores Estimated Cancer Incidence, Mortality and Prevalence Worldwide using data sourced from cancer registries of each country. 
The Bowel Cancer Australia Atlas in Figure 1<!--\ref{fig:choropleth-grid-create}-->d presents an example of a cancer specific atlas, it shows the average Standardized Incidence Ratio of colorectal cancer for Australian males from 2006 to 2010 in Australia [@Bowel]. Like many of the atlases examined, there is a choice of gender displayed in the Bowel Cancer Atlas. An alternative approach used in the Map of Cancer Mortality Rates in Spain, Figure 1<!--\ref{fig:choropleth-grid-create}-->f shows side-by-side maps of the relative risk of lung cancer separately for men and women [@cancerSpain].

There are vast differences in the geographies considered by online atlases. 
Figure 1<!--\ref{fig:choropleth-grid-create}-->b shows global age-standardized incidence rates (per 100,000) for all invasive cancers for both men and women, aggregated at a national level for 2018.
The United States Cancer Statistics [@USInteractive] presented in Figure 1<!--\ref{fig:choropleth-grid-create}-->e contains the incidence rate per 100,000, of all cancer types for men and women in the United States in 2016, aggregated at the state level.
The Environment and Health Atlas of England and Wales, Figure 1<!--\ref{fig:choropleth-grid-create}-->a shows the relative risk for women developing lung cancer in England and Wales in 2010 [@EnvEnglandWales2] at a neighborhood (small-area) scale.
The Atlas of Cancer in Queensland, Figure 1<!--\ref{fig:choropleth-grid-create}-->c shows the relative incidence ratio of lung cancer in males for each Statistical Area at Level 2 [@SA2] in the state of Queensland within Australia [@QLDcancerAtlas].

Age-specific atlases are less common, Figure 1<!--\ref{fig:choropleth-grid-create}-->g displays Atlas of Childhood Cancer in Ontario, this communicates the incidence rate of childhood cancers per 100,000 (by census division) for children aged 0-14, in Ontario from 1995 to 2004 [@OntarioPediatric]. This atlas communicates information regarding a small geographic region.

## Additional materials
<!-- 479 words -->
Cancer atlases often display supplementary graphs and plots to add more information. Additional materials such as tables, graphs, and text explanations support understanding and inference derived from maps, ensuring the message communicated will be consistent across a range of viewers [@CPISACA]. The many displays of statistical summaries, including dot plots, bar plots, box plots, cumulative distribution plots, scatter plots, and normal probability plots, can provide alternative views of the cancer statistics. These can also display supporting statistics such as error, confidence intervals, distributions, sample or population sizes, and standard deviation.

@@

Map users can define the population further using the demographics of the individuals within each area. Demographics that can influence cancer rates include information regarding the age and sex distribution of the areas presented. Some digital atlases surveyed allow users to control the display to select subsets such as males, females or those aged over 65. Similarly, socioeconomic indicators, such as unemployment rates, poverty rates, remoteness, and education levels, can explain how the experience of cancer prevalence varies for various members of society. Few atlases provide this
level of detail. Introducing population and demographic information helps to interpret the rates in areas effectively, but there will still be uncertainty around the rates. To address this, a cancer atlases often communicates uncertainty about the value of a statistic. There are several potential sources of uncertainty: sampling error, errors arising from the disease reporting process (or data collection), and errors arising from the statistical modeling or simulation process. The most common measures used to represent uncertainty were credible or confidence intervals (CIs). Displaying the uncertainty associated with reported statistics is a vital feature of a cancer map, but it is difficult to display effectively. The map focuses on displaying the statistic and lacks additional space to represent the uncertainty. Providing an adjacent map or overlaying maps with symbols [@VSSDCUC] are two approaches.

@@

Choropleth maps provide a familiar display that may be important for orienting a non-statistical audience. The familiar shape boundaries define individual areas of non-uniform size, containing different population densities and may be subject to change. A spatially heterogeneous population distribution across a country’s landmass is an issue common to many countries, especially British colonies [@ACTUC].

A disadvantage of the conventional map is that the different population and geographical sizes of administrative areas can attract attention to the shades of the underpopulated but large areas [@EI]. Skowronnek also [@BCM] discusses how choropleth maps suffer from area-size bias, as they give a 'stronger visual weight' to large  administrative units. The administrative boundaries used to define regions may limit a choropleth display, as this display unfaithfully represents the disease distribution across the region by obscuring small geographic areas. 
Sparsely populated rural areas are emphasized, whereas the areas representing inner city communities are very small.

Those who critique choropleth maps often discuss bi-partisan election mapping in the United States of America [@BCM, @NISCC].
Election mapping in Australia also suffers when presented on choropleth maps, where each electorate decides the outcome of one parliamentary seat in the house of representatives. While all states are visible on a map display of Australia, smaller geographic units such as electorates present an extreme case of an urban-rural divide. The landmass occupied by urban electoral districts is only 10% of Australia, yet 90% of the population live in these urban areas. To present election results on a choropleth map should be ‘unthinkable’, as it means diminishing the visual impact of most of the electorates and incorrectly communicating the distribution of votes across the country.

Choropleth maps can inhibit visual inference when presenting human-related statistics as the display may draw attention away from the ‘potentially more important results in the more populous communities’ that are geographically smaller [@SE]. 
Inset maps like in Brisbane city in Figure Figure 1<!--\ref{fig:choropleth-grid-create}-->c of the state of Queensland are commonly used to reduce distorted interpretations, but it is not always an appropriate solution. As this feature of population distributions continues to intensify, the need for cartograms as an alternative to a choropleth map should only increase.

@@

<!-- What is a cartogram? -->
Choropleth maps imply uniformity of data across the geographic space but population densities are unlikely to be uniform [@BCM]. Cartographers developed the cartogram to draw the attention to the population by transforming the map [@ACCAC]. The resulting display can communicate the impact of the disease more accurately across the population, as recorded by the statistic, at the sacrifice of geographic accuracy.
